### 2014-11-07 docs/ms.Rmd
Added figure 1 chunk to ms and also finished results section. Still need to add one more figure, plus fix up fig 1 and also add the additonal visual modelling stuff that Tom did in the text.

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies. Of the studies analysing their data using visual models, `r round(prop_vismod, digits = 2)`% reported the type of visual model they used while only `r round(prop_irrad, digits =2)`%  reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% reported the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods.

>>>>

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies. Of the studies analysing their data using visual models, `r round(prop_vismod, digits = 2)`% reported the type of visual model they used while only `r round(prop_irrad, digits =2)`%  reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% reported the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods. It is important to note that papers often made reference to previous work for various methods (`r ref_stud`%) and so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more careful and comprehensive reporting within studies.

```{r, eval = TRUE, echo = FALSE}

barplot(dat, ylim = c(0,100), ylab = "Percentages of studies reporting", xlab = "Criteria", col = "gray") -> bp.out
abline(h = 0, lwd = 2)
text(N_props, x = bp.out, y = 98)

```
